A Logical Solution of the Linearity Challenge

### 2025-08-02 paper/introduction.tex

The rest of the paper is structured as follows. \Cref{sec:calculus} describes
the syntax and the operational semantics of \Calculus and states the properties
of well-typed processes that we formalize and prove. \Cref{sec:agda} outlines
the essential aspects of the formalization with particular emphasis on the
representation of channel names and typing contexts. \Cref{sec:conclusion}
summarizes our contributions, discusses some extensions and future work. The
formalization has been carried out using Agda and its full code is available
from a public
repository.\footnote{\url{https://github.com/boystrange/LinearityChallenge/tree/main/exp}}

>>>>

The rest of the paper is structured as follows. \Cref{sec:calculus} describes
the syntax and the operational semantics of \Calculus and states the properties
of well-typed processes that we formalize and prove. \Cref{sec:agda} outlines
the essential aspects of the formalization with particular emphasis on the
representation of channel names and typing contexts. \Cref{sec:conclusion}
summarizes our contributions, discusses some extensions and future work. The
formalization has been carried out using Agda and its full code is available
from a public\Luca{Related work? Confronto con altre formalizzazioni?}
repository.\footnote{\url{https://github.com/boystrange/LinearityChallenge/tree/main/exp}}
